\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Imitation Learning data collection using Apple Vision Pro}
\author{Mmanu Chaturvedi}
\date{January 2026}

\begin{document}

\maketitle

\section{Introduction}
Imitation learning is a process of learning a robot policy with demonstration.  There is a scarcity of data for imitation learning because freely available
data on the internet is not useful for this.  This project aims to collect data using Apple Vision Pro (AVP) that can be used for training machine learning
algorithm for imitation learning.  We write an AVP application that can be used to collect the camera images, head and hand pose.  This
data is to be used for training algorithms for controlling robots.


\section{Previous work}
There are a few datasets availabel that capture data for imitation learning.  Datasets like Egodex[], [Add more here], that collect data for imitation learning. We collect data in a way that Egodex does, i.e., using a VR headset by Apple, AVP.


\section{Apple Vision Pro description}
AVP has a lot of sensors which have no official description or documentation.   The ones that do are the left and right main cameras, which can be captured from [TODO: cite]

\section{Data format}
\begin{enumerate}
	\item JSON file:  Data is colleted in JSON format for head and hand pose.
	\item JPEG file: Images are captured from the left and right cameras of AVP.
\end{enumerate}




% https://developer.apple.com/documentation/visionOS/accessing-the-main-camera


\end{document}

